Effects of Reynolds Number on the Performance and Near-Wake of a Vertical-Axis Cross-Flow Turbine

### 2015-04-08 paper.tex
Add Chamorro et al reference for AFT wake

\subsection{Reynolds Number Effects}
\todo[inline]{Add lit review here}

@@

@@

\begin{figure}[ht]
\centering
\includegraphics[width=0.65\textwidth]{figures/cft_re_dep_foils}
\caption{Reynolds number depenence of the peak torque coefficient calculated via
static foil coefficients and blade kinematics.}
\label{fig:foils-C_T-Re-dep}
\end{figure}

>>>>

\subsection{Reynolds Number Effects}

@@

Chamorro et al. showed that turbulence statistics in an AFT wake became
$Re$-independent at $Re_D \approx 1 \times 10^5$, with mean velocity slightly
earlier at $Re_D \approx 5 \times 10^4$ \cite{Chamorro2012}.

@@

\begin{figure}[ht]
\centering
\includegraphics[width=0.65\textwidth]{figures/cft_re_dep_foils}
\caption{Reynolds number dependence of the peak torque coefficient calculated using 
only static foil coefficients and blade kinematics.}
\label{fig:foils-C_T-Re-dep}
\end{figure}
